PM Component Paper Plots

### 2021-10-07 code/data-viz/forest-plots-color-shape.Rmd
revision

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-mass-ses.RDa'))
#load(here('output','analysis','out-fac-base-ec.RDa'))
#load(here('output','analysis','out-fac-ses-ec.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
```

```{r set theme 1 - single group plots}
ggtheme.single <- theme_bw() + 
  theme(panel.spacing.x = unit(0.5, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, face = 'bold', color = 'black'),
  )
```

```{r set theme 2 - components - effect modification, subgroups, multiple groups plots}
ggtheme.multi.1 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.5,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r set theme 3 - factors - effect modification, subgroups, multiple groups plots}
ggtheme.multi.2 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.5,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = "bold", color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

@@

```{r - Components Base}
data <- out.pmc.base %>% 
  filter(Index %in% cmp.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

```{r - Components SES-Adj}
data <- out.pmc.ses %>% 
  filter(Index %in% cmp.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

```{r - Factor Base}
data <- out.fac.base %>% 
  filter(Index %in% So.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

```{r - Factor SES-Adj}
data <- out.fac.ses %>% 
  filter(Index %in% So.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

```{r - App Mass SES-Adj}
data <- out.mass.ses %>% 
  filter(Index %in% So.main,
         Cause %in% cuz,
         HR < 5,
         HR.U < 5) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

```{r - Components - PM Residual}
data <- out.pmc.resid %>% 
  filter(Index %in% cmp.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.res),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

```{r - Factor - PM Residual}
data <- out.fac.resid %>% 
  filter(Index %in% So.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.res),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

```{r - Components Age}
data <- out.pmc.age %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Age == "LE75", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Age == "M75"), 1,
                      ifelse((sig == 15 & Age == "M75"),16, sig)),
         sig = as.integer(sig)
  )

@@

```{r - Factor Age}
data <- out.fac.age %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Age == "LE75", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Age == "M75"), 1,
                      ifelse((sig == 15 & Age == "M75"),16, sig)),
         sig = as.integer(sig)
  )

@@

```{r - Components Sex}
data <- out.pmc.sex %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Sex == "F", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Sex == "M"), 1,
                      ifelse((sig == 15 & Sex == "M"),16, sig)),
         sig = as.integer(sig)
  )

@@

```{r - Factor Sex}
data <- out.fac.sex %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Sex == "F", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Sex == "M"), 1,
                      ifelse((sig == 15 & Sex == "M"),16, sig)),
         sig = as.integer(sig)
  )

@@

```{r - Components Race}
data <- out.pmc.race %>% 
  arrange(Index, Cause, Race) %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Race == "A", "d",
                      ifelse(Race == "B", "c",
                             ifelse(Race == "H", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1, 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Race == "W"), 5,
                      ifelse((sig == 15 & Race == "W"), 18, sig)),
         sig = ifelse((sig == 0 & Race == "H"), 2,
                      ifelse((sig == 15 & Race == "H"), 17, sig)),
         sig = ifelse((sig == 0 & Race == "B"), 1,
                      ifelse((sig == 15 & Race == "B"), 16, sig)),
         sig = as.integer(sig)
  )

@@

```{r - Factor Race}
data <- out.fac.race %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Race == "A", "dd",
                      ifelse(Race == "B", "cc",
                             ifelse(Race == "H", "bb", "aa"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Race == "W"), 5,
                      ifelse((sig == 15 & Race == "W"),18, sig)),
         sig = ifelse((sig == 0 & Race == "H"), 2,
                      ifelse((sig == 15 & Race == "H"),17, sig)),
         sig = ifelse((sig == 0 & Race == "B"), 1,
                      ifelse((sig == 15 & Race == "B"),16, sig)),
         sig = as.integer(sig)
  )

@@

```{r Components Urbanicity}
data <- out.pmc.urbanicity %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Loc.Set == "urban", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Loc.Set == "rural"), 1,
                      ifelse((sig == 15 & Loc.Set == "rural"),16, sig)),
         sig = as.integer(sig)
  )

@@

```{r - Factor Urbanicity}
data <- out.fac.urbanicity %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Loc.Set == "urban", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Loc.Set == "rural"), 1,
                      ifelse((sig == 15 & Loc.Set == "rural"),16, sig)),
         sig = as.integer(sig)
  )

@@

```{r - Components urban}
data <- out.pmc.urbanicity %>% 
  filter(Loc.Set == "urban") %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = rev(cmp.multi)),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

```{r Components SES-Urban}
data <- out.pmc.sescat %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(SES.Cat == "L", "c",
                      ifelse(SES.Cat == "M", "b", "a")),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & SES.Cat == "H"), 2,
                      ifelse((sig == 15 & SES.Cat == "H"),17, sig)),
         sig = ifelse((sig == 0 & SES.Cat == "M"), 1,
                      ifelse((sig == 15 & SES.Cat == "M"),16, sig)),
         sig = as.integer(sig)
  )

@@

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-sescat.jpeg'), width = 7.5, height = 7.5, dpi = 600)
```

```{r - Components Region}
data <- out.pmc.region %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Region == "west", "d",
                      ifelse(Region == "midwest", "c",
                             ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.integer(sig)
  )

>>>>

```{r Load data}
load(here('output','analysis','out-pmc-base.RDa'))
load(here('output','analysis','out-pmc-ses.RDa'))
load(here('output','analysis','out-fac-base.RDa'))
load(here('output','analysis','out-fac-ses.RDa'))
load(here('output','analysis','out-mass-ses.RDa'))
load(here('output','analysis','out-mass-fac-ses.RDa'))
#load(here('output','analysis','out-fac-base-ec.RDa'))
#load(here('output','analysis','out-fac-ses-ec.RDa'))
load(here('output','analysis','out-pmc-resid.RDa'))
load(here('output','analysis','out-fac-resid.RDa'))
load(here('output','analysis','out-pmc-age.RDa'))
load(here('output','analysis','out-fac-age.RDa'))
load(here('output','analysis','out-pmc-sex.RDa'))
load(here('output','analysis','out-fac-sex.RDa'))
load(here('output','analysis','out-pmc-race.RDa'))
load(here('output','analysis','out-fac-race.RDa'))
load(here('output','analysis','out-pmc-urbanicity.RDa'))
load(here('output','analysis','out-fac-urbanicity.RDa'))
load(here('output','analysis','out-pmc-sescat.RDa'))
load(here('output','analysis','out-pmc-region.RDa'))
load(here('output','analysis','out-pmc-resid-region.RDa'))
load(here('output','analysis','out-fac-region.RDa'))
load(here('output','analysis','out-pmc-brfss.RDa'))
load(here('output','analysis','out-pmc-buffer.RDa'))
load(here('output','analysis','out-pmc-expo.RDa'))
load(here('output','analysis','out-pmc-buffer-expo.RDa'))
```

```{r set theme 1 - single group plots}
ggtheme.single <- theme_bw() + 
  theme(panel.spacing.x = unit(0.5, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title.x = element_text(size = 10, color = 'black'),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 8, color = 'black')
  )
```

```{r set theme 2 - components - effect modification, subgroups, multiple groups plots}
ggtheme.multi.1 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.5,'lines'),
        panel.spacing.y = unit(c(0.25,0,0.25,0,0.25,0,0.25,0,0.25,0),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title.x = element_text(size = 10, color = 'black'),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r set theme 3 - factors - effect modification, subgroups, multiple groups plots}
ggtheme.multi.2 <- theme_classic() + 
  theme(panel.spacing.x = unit(0.5,'lines'),
        panel.spacing.y = unit(c(0.25),'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, color = "black", angle = 180),
        strip.text.y.left = element_text(angle = 0),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.title.x = element_text(size = 10, color = 'black'),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        legend.position = 'bottom',
        legend.title = element_blank(),
        legend.text = element_text(size = 10, face = "bold"),
        legend.key.width = unit(0.25, units = 'in'))
```

```{r set theme 4 - matrix plots}
ggtheme.matrix <- theme_bw() + 
  theme(panel.spacing.x = unit(0.25, 'lines'),
        panel.border = element_rect(fill = NA, 'lines', color = "gray25"),
        strip.text.x = element_text(size = 10, face = 'bold', color = "black"),
        strip.text.y = element_text(size = 10, face = 'bold', color = "black"),
        strip.background = element_rect(fill = "#B9CFED"),
        axis.text.x = element_text(size = 8, color = 'black'),
        axis.text.y = element_text(size = 9, color = 'black'),
        legend.position = 'right',
        legend.title = element_blank(),
        legend.text = element_text(size = 9, face = "bold"),
        legend.key.width = unit(0.25, units = 'in')
  )
```

@@

<br>

### Components Base
```{r - Components Base, fig.dim = c(7.5, 6.5)}
data <- out.pmc.base %>% 
  filter(Index %in% cmp.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

<br>

### Components SES
```{r - Components SES-Adj, fig.dim = c(7.5, 6.5)}
data <- out.pmc.ses %>% 
  filter(Index %in% cmp.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

<br>

### Factors Base
```{r - Factor Base, fig.dim = c(7.5, 6.5)}
data <- out.fac.base %>% 
  filter(Index %in% So.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

<br>

### Factors SES
```{r - Factor SES-Adj, fig.dim = c(7.5, 6.5)}
data <- out.fac.ses %>% 
  filter(Index %in% So.main,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

<br>

### Mass
```{r - App Mass SES-Adj, fig.dim = c(7.5, 6.5)}
data <- out.mass.ses %>% 
  filter(Index %in% So.main,
         Cause %in% cuz,
         HR < 5,
         HR.U < 5) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

<br>

### Mass Factor
```{r - App Mass Factor SES-Adj, fig.dim = c(7.5, 6.5)}
data <- out.mass.fac.ses %>% 
  filter(Index %in% So.main,
         Cause %in% cuz,
         HR < 5,
         HR.U < 5) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','mass-fac-ses.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### PM-Components Residual
```{r - Components - PM Residual, fig.dim = c(7.5, 6.5)}
data <- out.pmc.resid %>% 
  filter(Index %in% cmp.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.res),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

<br>

### PM-Factors Residual
```{r - Factor - PM Residual, fig.dim = c(7.5, 6.5)}
data <- out.fac.resid %>% 
  filter(Index %in% So.res,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.res),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

<br>

### Components Age
```{r - Components Age, fig.dim = c(7.5, 7.5)}
data <- out.pmc.age %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Age == "LE75", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Age == "M75"), 1,
                      ifelse((sig == 15 & Age == "M75"),16, sig)),
         sig = as.integer(sig)
  )

@@

<br>

### Factors Age
```{r - Factor Age, fig.dim = c(7.5, 6.5)}
data <- out.fac.age %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Age == "LE75", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Age == "M75"), 1,
                      ifelse((sig == 15 & Age == "M75"),16, sig)),
         sig = as.integer(sig)
  )

@@

<br>

### Components Sex
```{r - Components Sex, fig.dim = c(7.5, 7.5)}
data <- out.pmc.sex %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Sex == "F", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Sex == "M"), 1,
                      ifelse((sig == 15 & Sex == "M"),16, sig)),
         sig = as.integer(sig)
  )

@@

<br>

### Factors Sex
```{r - Factor Sex, fig.dim = c(7.5, 6.5)}
data <- out.fac.sex %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Sex == "F", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Sex == "M"), 1,
                      ifelse((sig == 15 & Sex == "M"),16, sig)),
         sig = as.integer(sig)
  )

@@

<br>

### Components Race
```{r - Components Race, fig.dim = c(7.5, 8.5)}
data <- out.pmc.race %>% 
  arrange(Index, Cause, Race) %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Race == "A", "d",
                      ifelse(Race == "B", "c",
                             ifelse(Race == "H", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1, 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Race == "W"), 5,
                      ifelse((sig == 15 & Race == "W"), 18, sig)),
         sig = ifelse((sig == 0 & Race == "H"), 2,
                      ifelse((sig == 15 & Race == "H"), 17, sig)),
         sig = ifelse((sig == 0 & Race == "B"), 1,
                      ifelse((sig == 15 & Race == "B"), 16, sig)),
         sig = as.integer(sig)
  )

@@

<br>

### Factors Race
```{r - Factor Race, fig.dim = c(7.5, 6.5)}
data <- out.fac.race %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Race == "A", "dd",
                      ifelse(Race == "B", "cc",
                             ifelse(Race == "H", "bb", "aa"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Race == "W"), 5,
                      ifelse((sig == 15 & Race == "W"),18, sig)),
         sig = ifelse((sig == 0 & Race == "H"), 2,
                      ifelse((sig == 15 & Race == "H"),17, sig)),
         sig = ifelse((sig == 0 & Race == "B"), 1,
                      ifelse((sig == 15 & Race == "B"),16, sig)),
         sig = as.integer(sig)
  )

@@

<br>

### Components Urbanicity
```{r Components Urbanicity, fig.dim = c(7.5, 7.5)}
data <- out.pmc.urbanicity %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Loc.Set == "urban", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Loc.Set == "rural"), 1,
                      ifelse((sig == 15 & Loc.Set == "rural"),16, sig)),
         sig = as.integer(sig)
  )

@@

<br>

### Factors Urbanicity
```{r - Factor Urbanicity, fig.dim = c(7.5, 6.5)}
data <- out.fac.urbanicity %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.multi),
         Tag = ifelse(Loc.Set == "urban", "b", "a"),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Loc.Set == "rural"), 1,
                      ifelse((sig == 15 & Loc.Set == "rural"),16, sig)),
         sig = as.integer(sig)
  )

@@

<br>

### Components Urban
```{r - Components urban, fig.dim = c(7.5, 6.5)}
data <- out.pmc.urbanicity %>% 
  filter(Loc.Set == "urban") %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = rev(cmp.multi)),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

@@

<br>

### Factors Urban
```{r - Factor Urban, fig.dim = c(7.5, 6.5)}
data <- out.fac.urbanicity %>%
  filter(Loc.Set == "urban") %>% 
  filter(Index %in% So.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = So.main),
         sig = ifelse(HR.U < 1 , 16, #16-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 1, 16)) #1-null #16-sigpos
  )

Plot.Single(dt = data, ggtheme = ggtheme.single) +
ggsave(here('output','plot','fac-urban.jpeg'), width = 7.5, height = 6.5, dpi = 600)
```

<br>

### Components SES-urban
```{r Components SES-Urban, fig.dim = c(7.5, 7.5)}
data <- out.pmc.sescat.upd %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(SES.Cat == "L", "c",
                      ifelse(SES.Cat == "M", "b", "a")),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & SES.Cat == "H"), 2,
                      ifelse((sig == 15 & SES.Cat == "H"),17, sig)),
         sig = ifelse((sig == 0 & SES.Cat == "M"), 1,
                      ifelse((sig == 15 & SES.Cat == "M"),16, sig)),
         sig = as.integer(sig)
  )

@@

Plot.Multi.lab(dt = data, ggtheme = ggtheme.multi.1, n = 1) +
ggsave(here('output', 'plot','pmc-sescat-upd.jpeg'), width = 7.5, height = 7.5, dpi = 600)
```

<br>

### Components Region
```{r - Components Region, fig.dim = c(7.5, 8.5)}
data <- out.pmc.region %>% 
  filter(Index %in% cmp.multi,
         Cause %in% cuz) %>% 
  mutate(Cause = factor(Cause, levels = cuz),
         Index = factor(Index, levels = cmp.multi),
         Tag = ifelse(Region == "west", "d",
                      ifelse(Region == "midwest", "c",
                             ifelse(Region == "south", "b", "a"))),
         Tag = as.factor(Tag),
         sig = ifelse(HR.U < 1 , 15, #15-prtc
                      ifelse((HR.L<=1 & HR.U>=1), 0, 15)), #0-null #15-sigpos
         sig = ifelse((sig == 0 & Region == "northeast"), 5,
                      ifelse((sig == 15 & Region == "northeast"),18, sig)),
         sig = ifelse((sig == 0 & Region == "south"), 2,
                      ifelse((sig == 15 & Region == "south"),17, sig)),
         sig = ifelse((sig == 0 & Region == "midwest"), 1,
                      ifelse((sig == 15 & Region == "midwest"),16, sig)),
         sig = as.integer(sig)
  )
